An Audio-Based 3D Spatial Guidance AR System for Blind Users

### 2020-05-30 Manuscript.Rmd
Updated template with \thanks

---
title: "An Audio-Based 3D Spatial Guidance AR System for Blind Users"
titlerunning: Audio-Based 3D Spatial Guidance
authorrunning: J. Couhlan et al.
output:
  pdf_document:
    template: res/templates/markdown.tex
    toc: no
    keep_tex: yes
institutes:
- id: 1
  name: The Smith-Kettlewell Eye Research Institute, San Francisco, CA
  emails: coughlan@ski.org, brandon.biggs@ski.org, hshen@ski.org
- id: 2
  name: LITIS, University of Rouen, Normandy, France
  emails: marc-aurele.riviere@univ-rouen.fr
keywords:
- Assisitive Devices
- Augmented Reality
- Auditory Substitution
- Visual Impairment
abstract: Augmented reality (AR) has great potential for blind users because it enables
  a range of applications that provide audio information about specific locations
  or directions in the user’s environment. For instance, the CamIO (“Camera Input-Output”)
  AR app makes physical objects (such as documents, maps, devices and 3D models) accessible
  to blind and visually impaired persons by providing real-time audio feedback in
  response to the location on an object that the user is touching (using an inexpensive
  stylus). An important feature needed by blind users of AR apps such as CamIO is
  a 3D spatial guidance feature that provides real-time audio feedback to help the
  user find a desired location on an object. We have devised a simple audio interface
  to provide verbal guidance towards a target of interest in 3D. The experiment we
  report with blind participants using this guidance interface demonstrates the feasibility
  of the approach and its benefit for helping users find locations of interest.
authors:
- name: James Coughlan
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Brandon Biggs
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Marc-Aurèle Rivière
  orcid: 0000-0002-5108-3382
  inst: 2
- name: Huiying Shen
  orcid: 0000-1111-2222-3333
  inst: 1
ressources: res/
templates: res/templates/
bibliography: res/refs.bib
---

>>>>

---
title: "An Audio-Based 3D Spatial Guidance AR System for Blind Users"
titlerunning: Audio-Based 3D Spatial Guidance
authorrunning: J. Couhlan et al.
thanks: Merci !
output:
  pdf_document:
    template: res/templates/template.tex
    toc: no
    keep_tex: yes
  word_document:
    reference_docx: res/templates/template.docx
    toc: no
institutes:
- id: 1
  name: The Smith-Kettlewell Eye Research Institute, San Francisco, CA
  emails: coughlan@ski.org, brandon.biggs@ski.org, hshen@ski.org
- id: 2
  name: LITIS, University of Rouen, Normandy, France
  emails: marc-aurele.riviere@univ-rouen.fr
keywords:
- Assisitive Devices
- Augmented Reality
- Auditory Substitution
- Visual Impairment
abstract: Augmented reality (AR) has great potential for blind users because it enables
  a range of applications that provide audio information about specific locations
  or directions in the user’s environment. For instance, the CamIO (“Camera Input-Output”)
  AR app makes physical objects (such as documents, maps, devices and 3D models) accessible
  to blind and visually impaired persons by providing real-time audio feedback in
  response to the location on an object that the user is touching (using an inexpensive
  stylus). An important feature needed by blind users of AR apps such as CamIO is
  a 3D spatial guidance feature that provides real-time audio feedback to help the
  user find a desired location on an object. We have devised a simple audio interface
  to provide verbal guidance towards a target of interest in 3D. The experiment we
  report with blind participants using this guidance interface demonstrates the feasibility
  of the approach and its benefit for helping users find locations of interest.
authors:
- name: James Coughlan
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Brandon Biggs
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Marc-Aurèle Rivière
  orcid: 0000-0002-5108-3382
  inst: 2
- name: Huiying Shen
  orcid: 0000-1111-2222-3333
  inst: 1
ressources: res/
templates: res/templates/
bibliography: res/refs.bib
---
